---
title: "Breast Cancer Risk in Twin Cohorts"
subtitle: "Cox Proportional Hazards Models with Menopausal Time-Splitting"
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: true
    code-summary: "Show code"
    embed-resources: true
editor: visual
---

## Setup

```{r setup}
#| label: setup

knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 6
)

library(dplyr)
library(tidyr)
library(survival)
library(tidyverse)
library(broom)
library(flextable)
library(officer)
library(ggplot2)
library(gtsummary)
library(table1)
library(survminer)
```

## Overview

This document builds the analytic cohort from the raw twin registry data, constructs two versions of the exposure variable for dizygotic (DZ) twins — one keeping the co-twin's sex separate, one combining male and female co-twins — and fits Cox proportional hazards models for breast cancer (BC) risk. Menopausal status is treated as a time-varying covariate via time-splitting.

All downstream tables and forest plots are restricted to the **DZ cohorts vs. the non-twin reference group**, since these were the only comparisons requiring further analysis.

## 1. Data Loading and Cohort Construction

```{r load-data}
#| label: load-data

load("dr00368_01_01.Rdata")
unfiltered_data <- as_tibble(sas)
```

### 1.1 Apply inclusion/exclusion criteria

Exclusions: prevalent BC at baseline, triplets+, no full BC-affected sibling, unknown BC event status.

```{r build-cohort}
#| label: build-cohort

sas_tibble <- unfiltered_data %>%
  filter(is.na(FU_BCInvD_DxPrebaseline) | FU_BCInvD_DxPrebaseline == 0) %>%
  filter(F28fix <= 2 | is.na(F28fix)) %>%                      # remove triplets
  filter(!(SX_FullSisBC == 0 &
             (SX_FullSisBC_SameAge == 0 | is.na(SX_FullSisBC_SameAge)))) %>%
  filter(!is.na(FU_BCInvD_Event)) %>% #incomplete BC information
  mutate(monozygotic = case_when(
    F32fix == 1 | F38fix == 1 ~ 1,   # genetic test confirmed identical
    F32fix == 2 | F38fix == 2 ~ 0,   # genetic test confirmed non-identical
    F30fix == 1 | F36fix == 1 ~ 1,   # no test, but believes identical
    F30fix == 0 | F36fix == 0 ~ 0,   # no test, but believes nonidentical
    is.na(F32fix) & is.na(F38fix) & is.na(F30fix) & is.na(F36fix) &
      F28fix == 2 ~ 0,
    .default = NA_real_
  )) %>%
  select(PSID, Maternal_age1 = F2Age_v1, Maternal_age2 = F2Age_v2,
         Paternal_age1 = F16Age_v1, Paternal_age2 = F16Age_v2,
         Birth_weight = F20Weight, Baseline_Year, Birth_Year,
         EX_Visit_AgeExact, Bayesian_fam_history = BFHS,
         Lifetime_Risk = BOADICEA_BC_LT_V2, FU_BCInvD_DxAgeExact,
         FU_BCInvD_EOFAgeExact, FU_BCInvD_Event, FU_BC_PrimaryCOD,
         FU_BC_NDIDC_Conf, everything())
```

### 1.2 Define the eight zygosity/exposure cohorts

```{r cohorts}
#| label: cohorts

cohort1 <- sas_tibble %>%
  filter(monozygotic == 1, SX_FullSisBC_SameAge >= 1)               # MZ, co-twin BC

cohort2 <- sas_tibble %>%
  filter(monozygotic == 0, F29fix != 1 | is.na(F29fix),
         SX_FullSisBC_SameAge == 0, SX_FullSisBC >= 1)              # DZ, co-twin unaffected, another sister affected

cohort3 <- sas_tibble %>%
  filter(monozygotic == 0 | is.na(monozygotic),
         SX_FullSisBC_SameAge >= 1)  # DZ, co-twin BC                                   # DZ, co-twin BC

cohort4 <- sas_tibble %>%
  filter(F27fix == 1 | is.na(F27fix), SX_FullSisBC >= 1)# non-twin, affected full sister

cohort5 <- sas_tibble %>%
  filter(monozygotic == 1 & SX_FullSisBC_SameAge == 0 & SX_FullSisBC >= 1)  # MZ, co-twin unaffected, another sister affected

cohort6 <- sas_tibble %>%
  filter(F29fix == 1, SX_FullSisBC_SameAge == 0)                # DZ, male co-twin

cohort7 <- sas_tibble %>%
  filter((F32fix == 1 | F38fix == 1) &
           !is.na(SX_FullSisBC_SameAge) & SX_FullSisBC_SameAge >= 1)  # confirmed MZ, co-twin BC

cohort8 <- sas_tibble %>%
  filter((F32fix == 1 | F38fix == 1) &
           !is.na(SX_FullSisBC_SameAge) & SX_FullSisBC_SameAge == 0 &
           !is.na(SX_FullSisBC) & SX_FullSisBC >= 1)  # confirmed MZ, co-twin unaffected

cat(
  "Cohort 1 - MZ, co-twin BC:                        ", nrow(cohort1), "\n",
  "Cohort 2 - DZ, co-twin unaffected, sister BC:      ", nrow(cohort2), "\n",
  "Cohort 3 - DZ, co-twin BC:                         ", nrow(cohort3), "\n",
  "Cohort 4 - Non-twin, affected full sister:          ", nrow(cohort4), "\n",
  "Cohort 5 - MZ, co-twin unaffected, sister BC:       ", nrow(cohort5), "\n",
  "Cohort 6 - DZ, male co-twin:                        ", nrow(cohort6), "\n",
  "Cohort 7 - Confirmed MZ, co-twin BC:                ", nrow(cohort7), "\n",
  "Cohort 8 - Confirmed MZ, co-twin unaffected:        ", nrow(cohort8), "\n",
  "Total (cohorts 1-6):                                ", nrow(cohort1) + nrow(cohort2) + nrow(cohort3) + nrow(cohort4) + nrow(cohort5) + nrow(cohort6), "\n",
  sep = ""
)

```

```{r cohort-column}
#| label: cohort-column

sas_tibble <- sas_tibble %>%
  mutate(cohort = case_when(
    PSID %in% cohort7$PSID                            ~ 7,
    PSID %in% cohort8$PSID                            ~ 8,
    PSID %in% cohort1$PSID & !PSID %in% cohort7$PSID  ~ 1,
    PSID %in% cohort2$PSID                            ~ 2,
    PSID %in% cohort3$PSID                            ~ 3,
    PSID %in% cohort4$PSID                            ~ 4,
    PSID %in% cohort5$PSID & !PSID %in% cohort8$PSID  ~ 5,
    PSID %in% cohort6$PSID                            ~ 6,
    TRUE                                               ~ NA_real_
  ))
```

### 1.3 Cohort summary table

```{r cohort-summary}
#| label: cohort-summary

cohort_summary <- tibble(
  Cohort = 1:8,
  Description = c(
    "MZ twins, co-twin had BC",
    "DZ twins, co-twin did NOT have BC but another full sister did",
    "DZ twins, co-twin DID have BC",
    "Non-twins, affected full sister (reference)",
    "MZ twins, co-twin did NOT have BC but another affected sister did",
    "DZ twins, co-twin is male",
    "Confirmed MZ twins, co-twin had BC",
    "Confirmed MZ twins, co-twin did NOT have BC"
  ),
  N = c(nrow(cohort1), nrow(cohort2), nrow(cohort3), nrow(cohort4),
        nrow(cohort5), nrow(cohort6), nrow(cohort7), nrow(cohort8)),
  BC_Cases = c(
    sum(cohort1$FU_BCInvD_Event == 1, na.rm = TRUE),
    sum(cohort2$FU_BCInvD_Event == 1, na.rm = TRUE),
    sum(cohort3$FU_BCInvD_Event == 1, na.rm = TRUE),
    sum(cohort4$FU_BCInvD_Event == 1, na.rm = TRUE),
    sum(cohort5$FU_BCInvD_Event == 1, na.rm = TRUE),
    sum(cohort6$FU_BCInvD_Event == 1, na.rm = TRUE),
    sum(cohort7$FU_BCInvD_Event == 1, na.rm = TRUE),
    sum(cohort8$FU_BCInvD_Event == 1, na.rm = TRUE)
  )
)
```

## 2. Exposure Variable Construction

### 2.1 Separate DZ male/female co-twin (`dat_all_sep`)

```{r exposure-sep}
#| label: exposure-sep

dat_all_sep <- sas_tibble %>%
  mutate(
    exposure = case_when(
      PSID %in% cohort7$PSID                            ~ "MZ_confirmed_BC",
      PSID %in% cohort3$PSID                            ~ "DZ_BC",
      PSID %in% cohort1$PSID & !PSID %in% cohort7$PSID  ~ "Unk_zyg_BC",
      PSID %in% cohort8$PSID                            ~ "MZ_confirmed_noBC",
      PSID %in% cohort2$PSID                            ~ "DZ_noBC",
      PSID %in% cohort5$PSID & !PSID %in% cohort8$PSID  ~ "Unk_zyg_noBC",
      PSID %in% cohort4$PSID                            ~ "NonTwin_SisBC",
      PSID %in% cohort6$PSID                            ~ "DZ_noBC_Male_co-twin",
      TRUE ~ NA_character_
    ),
    exposure_f = relevel(factor(exposure), ref = "NonTwin_SisBC")
  ) %>%
  filter(!is.na(exposure))
  #filter(!is.na(EX_BMI_final))

dat_all_sep %>%
  count(exposure) %>%
  arrange(match(exposure, c(
    "MZ_confirmed_BC", "DZ_BC", "Unk_zyg_BC", "MZ_confirmed_noBC",
    "DZ_noBC", "Unk_zyg_noBC", "NonTwin_SisBC", "DZ_noBC_Male_co-twin"
  )))
```

```{r missingness}
#| label: missingness

covariates <- c("EX_BMI_final", "Bayesian_fam_history")

dat_all_sep %>%
  group_by(exposure) %>%
  summarise(
    N = n(),
    across(all_of(covariates), ~ sum(is.na(.)), .names = "miss_{.col}"),
    .groups = "drop"
  )
```

## 3. Menopause Variable Construction

The following logic is applied to the exposure dataset (`dat_all_sep`) to build menopausal age/status and then time-split each person into pre- and post-menopausal intervals.

```{r meno-function}
#| label: meno-function

build_dat_meno <- function(dat) {
  dat %>%
    mutate(
      BC_Event = FU_BCInvD_Event,

      # Menopausal age: exact if available, fall back to integer age
      menoage = FU_BCInvD_MenopauseAgeExact,
      menoage = case_when(
        is.na(menoage) & !is.na(FU_BCInvD_MenopauseAge) &
          FU_BCInvD_MenopauseAge != as.integer(AgeExact_T0)
        ~ as.numeric(FU_BCInvD_MenopauseAge),
        is.na(menoage) & !is.na(FU_BCInvD_MenopauseAge) &
          FU_BCInvD_MenopauseAge == as.integer(AgeExact_T0) &
          FU_BCInvD_MenopauseStatus %in% c(6, 7, 11)
        ~ AgeExact_T0 + 0.9,
        is.na(menoage) & !is.na(FU_BCInvD_MenopauseAge) &
          FU_BCInvD_MenopauseAge == as.integer(AgeExact_T0) &
          (FU_BCInvD_MenopauseStatus %in% c(1, 3, 4, 5, 8, 9, 10) |
             is.na(FU_BCInvD_MenopauseStatus))
        ~ as.numeric(FU_BCInvD_MenopauseAge),
        TRUE ~ menoage
      ),

      # Earliest hysterectomy age across waves
      hyst_age_min = pmin(HR_HystAgeExact_T0, HR_HystAgeExact_T1,
                          HR_HystAgeExact_T2, HR_HystAgeExact_T3,
                          HR_HystAgeExact_T4, HR_HystAgeExact_T5, na.rm = TRUE),
      hyst_age_min = if_else(is.infinite(hyst_age_min), NA_real_, hyst_age_min),

      # EOF age censored at hysterectomy if hyst before EOF
      eof_age_imp_hyst = if_else(
        !is.na(hyst_age_min) & hyst_age_min < FU_BCInvD_EOFAgeExact,
        hyst_age_min, FU_BCInvD_EOFAgeExact
      ),

      # Baseline menopausal status (1 = post, 0 = pre)
      baseline_meno = case_when(
        !is.na(menoage) & menoage <= AgeExact_T0                     ~ 1,
        !is.na(menoage) & menoage >  AgeExact_T0                     ~ 0,
        is.na(menoage) & HR_MenopauseStatus_T0 %in% c(6, 7, 11, 9)   ~ 0,
        is.na(menoage) & HR_MenopauseStatus_T0 %in% c(1, 2, 3, 4, 5, 10) ~ 1,
        is.na(menoage) & (HR_MenopauseStatus_T0 == 8 | is.na(HR_MenopauseStatus_T0)) &
          FU_BCInvD_MenopauseStatus %in% c(6, 7, 11)                 ~ 0,
        TRUE ~ NA_real_
      ),

      # Impute menoage for those premenopausal at baseline
      menoage = case_when(
        is.na(menoage) & baseline_meno == 0 &
          FU_BCInvD_MenopauseStatus %in% c(1, 2, 3, 5, 8) &
          AgeExact_T0 < 55 & eof_age_imp_hyst >= 55                  ~ 55,
        is.na(menoage) & baseline_meno == 0 &
          FU_BCInvD_MenopauseStatus %in% c(1, 2, 3, 5, 8) &
          AgeExact_T0 >= 55                                          ~ AgeExact_T0 + 0.1,
        is.na(menoage) & baseline_meno == 0 &
          FU_BCInvD_MenopauseStatus %in% c(1, 2, 3, 5) &
          eof_age_imp_hyst < 55                                      ~ eof_age_imp_hyst - 0.1,
        is.na(menoage) & baseline_meno == 0 &
          FU_BCInvD_MenopauseStatus == 8 & eof_age_imp_hyst < 55     ~ NA_real_,
        TRUE ~ menoage
      ),

      # EOF menopausal status (1 = post by EOF, 0 = still pre)
      eof_meno = case_when(
        baseline_meno == 1                                              ~ 1,
        baseline_meno == 0 & !is.na(menoage) & menoage >  eof_age_imp_hyst ~ 0,
        baseline_meno == 0 & !is.na(menoage) & menoage <= eof_age_imp_hyst ~ 1,
        baseline_meno == 0 & FU_BCInvD_MenopauseStatus %in% c(6, 7, 11) ~ 0,
        TRUE ~ NA_real_
      ),
      eof_meno = replace(eof_meno, FU_BCInvD_MenopauseStatus == 9, 0),
      eof_meno = if_else(
        baseline_meno == 0 & FU_BCInvD_MenopauseStatus == 8 & eof_age_imp_hyst < 55,
        0, eof_meno
      ),

      # Did she transition during follow-up?
      postmeno_time = case_when(
        baseline_meno == 0 & eof_meno == 0 ~ 0,
        baseline_meno == 0 & eof_meno == 1 ~ 1,
        baseline_meno == 1                 ~ 1
      )
    )
}

build_meno_split <- function(dat_meno) {
  pre <- dat_meno %>%
    filter(baseline_meno == 0) %>%
    mutate(
      tstart  = AgeExact_T0,
      tstop   = if_else(eof_meno == 1, menoage, FU_BCInvD_EOFAgeExact),
      event3  = if_else(BC_Event == 1 & postmeno_time == 0, 1L, 0L),
      prepost = 0L
    )

  post <- dat_meno %>%
    filter(baseline_meno == 1 | (baseline_meno == 0 & eof_meno == 1)) %>%
    mutate(
      tstart  = if_else(baseline_meno == 1, AgeExact_T0, menoage),
      tstop   = FU_BCInvD_EOFAgeExact,
      event3  = if_else(BC_Event == 1 & postmeno_time == 1, 1L, 0L),
      prepost = 1L
    )

  combined <- bind_rows(pre, post)
  
  cat("Rows before final filter:", nrow(combined), "\n")
  cat("  Removed - tstart is NA:          ", sum(is.na(combined$tstart)), "\n")
  cat("  Removed - tstop is NA:           ", sum(is.na(combined$tstop)), "\n")
  cat("  Removed - tstop <= tstart:       ", sum(!is.na(combined$tstart) & 
                                                  !is.na(combined$tstop) & 
                                                  combined$tstop <= combined$tstart), "\n")
  
  result <- combined %>%
    filter(!is.na(tstart), !is.na(tstop), tstop > tstart) %>%
    mutate(prepost = factor(prepost, levels = c(0, 1),
                            labels = c("Premenopausal", "Postmenopausal")))
  
  cat("Rows after final filter:", nrow(result), "\n")
  cat("Total removed:", nrow(combined) - nrow(result), "\n")
  
  result
}
```

### 3.1 Apply to the DZ dataset

```{r meno-sep}
#| label: meno-sep

dat_meno_sep   <- build_dat_meno(dat_all_sep)
meno_split_sep <- build_meno_split(dat_meno_sep)

dat_meno_sep %>% summarise(
  n                  = n(),
  n_baseline_post    = sum(baseline_meno == 1, na.rm = TRUE),
  n_baseline_pre     = sum(baseline_meno == 0, na.rm = TRUE),
  n_transitioned     = sum(baseline_meno == 0 & eof_meno == 1, na.rm = TRUE),
  n_stayed_pre       = sum(baseline_meno == 0 & eof_meno == 0, na.rm = TRUE),
  n_missing_baseline = sum(is.na(baseline_meno)),
  n_missing_eof      = sum(is.na(eof_meno))
)


```

## 4. Cox models

### 4.1 Separate DZ male/female co-twin dataset and model

```{r}
# Separate DZ male/female co-twin version
meno_split_sep_dz <- meno_split_sep %>%
  filter(exposure_f %in% c("NonTwin_SisBC", "DZ_BC", "DZ_noBC",
                            "DZ_noBC_Male_co-twin")) %>%
  droplevels()

table(meno_split_sep_dz$exposure_f)

meno_split_sep_dz %>%
  group_by(exposure_f) %>%
  summarise(
    n_distinct_PSID = n_distinct(PSID),
    n_BCInvD_Event = n_distinct(PSID[FU_BCInvD_Event == 1])
  )

cox_meno_sep_dzonly <- coxph(
  Surv(tstart, tstop, event3) ~
    exposure_f + 
    EX_BMI_final * prepost +
    Bayesian_fam_history,
  data = meno_split_sep_dz
)

```

### 4.2 Testing assumptions of Cox Model

```{r}
## 1. Proportional Hazards Assumption 
# Schoenfeld residuals test: tests whether scaled residuals for each
# covariate are correlated with time. A significant p-value (<0.05)
# suggests that covariate's effect is NOT constant over time (PH violated).

ph_test <- cox.zph(cox_meno_sep_dzonly)
print(ph_test)

ggcoxzph(ph_test, var = "Bayesian_fam_history")

## Extract Schoenfeld residuals from the fitted model -----------------------
ph_test <- cox.zph(cox_meno_sep_dzonly)

# cox.zph() stores the residuals as a matrix with time as an attribute
schoenfeld_df <- as.data.frame(ph_test$y)
schoenfeld_df$time <- ph_test$x
names(schoenfeld_df) <- c(colnames(ph_test$y), "time")

## Reshape to long format for faceted plotting 

schoenfeld_long <- schoenfeld_df %>%
  pivot_longer(
    cols = -time,
    names_to = "covariate",
    values_to = "residual"
  ) %>%
  mutate(
    # log transform: residuals can be negative, so take log of absolute
    # value and preserve the sign separately
    log_abs_residual = log(abs(residual)),
    sign = if_else(residual >= 0, "positive", "negative")
  )

## Checking only Bayesian_fam_history specifically 
schoenfeld_long %>%
  filter(covariate == "Bayesian_fam_history") %>%
  ggplot(aes(x = time, y = log_abs_residual)) +
  geom_point(alpha = 0.4, size = 1.5, color = "#2C7FB8") +
  geom_smooth(method = "loess", se = TRUE, color = "black", linewidth = 0.8) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray40") +
  labs(
    title = "Log-Transformed Schoenfeld Residuals: Bayesian Family History",
    x = "Time",
    y = "log(|Schoenfeld residual|)"
  ) +
  theme_minimal(base_size = 12)
```

## 5. Results and Figures

### 5.1 Table 1 — Baseline characteristics (DZ + singleton only)

```{r}
# Filter to the relevant exposure groups 
table1_data <- dat_all_sep %>%
  filter(exposure %in% c("DZ_BC", "DZ_noBC", "NonTwin_SisBC", "DZ_noBC_Male_co-twin")) %>%
  droplevels() %>%
  mutate(
    exposure_t1 = factor(
      exposure,
      levels = c("NonTwin_SisBC", "DZ_noBC", "DZ_noBC_Male_co-twin", "DZ_BC"),
      labels = c("Non-twin, sister with BC (reference)",
                 "DZ twin, female co-twin no BC",
                 "DZ twin, male co-twin no BC",
                 "DZ twin, co-twin had BC")
    )
  )

table(table1_data$exposure_t1)

# Build summary table 

table1 <- table1_data %>%
  select(exposure_t1, AgeExact_T0, EX_BMI_final, FU_BCInvD_MenopauseAgeExact) %>%
  tbl_summary(
    by = exposure_t1,
    statistic = list(
      all_continuous()  ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = all_continuous() ~ 2,
    missing = "ifany",
    missing_text = "Missing",
    label = list(
      AgeExact_T0                  ~ "Age at baseline, y",
      EX_BMI_final                 ~ "BMI, kg/m2",
      FU_BCInvD_MenopauseAgeExact  ~ "Age at menopause, y"
    )
  ) %>%
  add_overall() %>%
  modify_header(label ~ "**Characteristic**") %>%
  modify_footnote(everything() ~ NA) %>%
  as_flex_table()

# Apply formatting 
table1 <- table1 %>%
  flextable::bold(part = "all", bold = FALSE) %>%
  flextable::bg(bg = "white", part = "all") %>%
  flextable::font(fontname = "Times New Roman", part = "all") %>%
  flextable::fontsize(size = 10, part = "all") %>%
  flextable::border_remove() %>%
  flextable::hline_top(part = "header", border = fp_border(width = 1.5)) %>%
  flextable::hline_bottom(part = "header", border = fp_border(width = 1)) %>%
  flextable::set_caption(
    caption = as_paragraph(
      as_chunk(
        "Table 1. Baseline Characteristics of Dizygotic Twins and Non-twin Sisters, by Breast Cancer Exposure Group",
        props = fp_text_default(
          font.family = "Times New Roman",
          color = "black",
          bold = TRUE,
          font.size = 10
        )
      )
    )
  ) %>%
  flextable::width(j = 1, width = 1.5) %>%
  flextable::width(j = 2:6, width = 1.0)

table1

# Export 
sect_properties <- prop_section(
  page_size = page_size(orient = "portrait", width = 8.5, height = 11),
  page_margins = page_mar(top = 1, bottom = 1, left = 1, right = 1)
)

save_as_docx(table1, path = "table1.docx", pr_section = sect_properties)
```

### 5.2 Table 2 — Hazard ratios, DZ groups vs. singleton (separate, DZ-only model)

```{r table2-combined}
#| label: table2-sep

s_sep <- summary(cox_meno_sep_dzonly)

all_results_sep <- data.frame(
  Variable = rownames(s_sep$coefficients),
  HR       = s_sep$coefficients[, "exp(coef)"],
  lower    = s_sep$conf.int[, "lower .95"],
  upper    = s_sep$conf.int[, "upper .95"],
  p.value  = s_sep$coefficients[, "Pr(>|z|)"]
)

results_sep <- all_results_sep %>%
  filter(grepl("^exposure_fDZ", Variable)) %>%
  mutate(
    `HR (95% CI)` = sprintf("%.2f (%.2f to %.2f)", HR, lower, upper),
    `P value` = ifelse(p.value < .001, "<.001", sprintf("%.2f", p.value))
  ) %>%
  select(Variable, `HR (95% CI)`)

results_sep$Variable[results_sep$Variable == "exposure_fDZ_BC"] <-
  "DZ, affected co-twin"
results_sep$Variable[results_sep$Variable == "exposure_fDZ_noBC"] <-
  "DZ, unaffected co-twin (female)"
results_sep$Variable[results_sep$Variable == "exposure_fDZ_noBC_Male_co-twin"] <-
  "DZ, unaffected co-twin (male)"

# Rename Variable column header
names(results_sep)[names(results_sep) == "Variable"] <- "Characteristic"

ft_table2_sep <- flextable::flextable(results_sep) %>%
  flextable::bold(part = "all", bold = FALSE) %>%
  flextable::bg(bg = "white", part = "all") %>%
  flextable::font(fontname = "Times New Roman", part = "all") %>%
  flextable::fontsize(size = 12, part = "all") %>%
  flextable::border_remove() %>%
  flextable::hline_top(part = "header", border = fp_border(width = 1.5)) %>%
  flextable::hline_bottom(part = "header", border = fp_border(width = 1)) %>%
  flextable::set_caption(
  caption = as_paragraph(
    as_chunk(
      "Table 2 (Separate Model, DZ-only subset). Hazard Ratios for Breast Cancer Among Dizygotic Twins, Co-twin Sex Kept Separate (Referent: Singleton Sisters)",
      props = fp_text_default(
        font.family = "Times New Roman",
        color = "black",
        bold = TRUE,
        font.size = 10
      )
    )
  )
) %>%
  flextable::autofit()

ft_table2_sep

# Export 
sect_properties <- officer::prop_section(
  page_size = officer::page_size(orient = "portrait", width = 8.5, height = 8),
  page_margins = officer::page_mar(top = 1, bottom = 1, left = 1, right = 1)
)

save_as_docx(ft_table2_sep, path = "table2_sep.docx", pr_section = sect_properties)
```

### 5.3 Forest plot — DZ groups (combined, DZ-only model)

```{r forest-separate}
#| label: forest-separate

forest_data_sep <- all_results_sep %>%
  filter(grepl("^exposure_fDZ", Variable)) %>%
  mutate(
    Label = case_when(
      Variable == "exposure_fDZ_BC"                ~ "DZ, BC",
      Variable == "exposure_fDZ_noBC"               ~ "DZ, no BC (female co-twin)",
      Variable == "exposure_fDZ_noBC_Male_co-twin"  ~ "DZ, no BC (male co-twin)",
      TRUE ~ Variable
    ),
    sig      = if_else(p.value < .05, "sig", "ns"),
    hr_label = sprintf("%.2f (%.2f to %.2f)", HR, lower, upper)
  ) %>%
  rename(`Lower 95% CI` = lower, `Upper 95% CI` = upper)

# Add the reference group as an explicit HR = 1 row 
ref_row <- tibble(
  Variable       = "exposure_fNonTwin_SisBC",
  HR             = 1,
  `Lower 95% CI` = NA_real_,
  `Upper 95% CI` = NA_real_,
  p.value        = NA_real_,
  Label          = "Non-twin, sister with BC (ref)",
  sig            = "ref",
  hr_label       = "1.00 (Reference)"
)

forest_data_sep <- bind_rows(ref_row, forest_data_sep)

forest_data_sep$Label <- factor(
  forest_data_sep$Label,
  levels = rev(c("Non-twin, sister with BC (ref)", "DZ, BC",
                 "DZ, no BC (female co-twin)", "DZ, no BC (male co-twin)"))
)

forest_plot_sep <- ggplot(forest_data_sep, aes(x = HR, y = Label)) +
  geom_vline(xintercept = 1, linetype = "dashed", color = "black", linewidth = 0.4) +
  geom_errorbarh(aes(xmin = `Lower 95% CI`, xmax = `Upper 95% CI`),
                 height = 0.2, linewidth = 0.6, color = "black", na.rm = TRUE) +
  geom_point(aes(shape = sig), size = 3.5, color = "black", fill = "black", stroke = 0.8) +
  geom_text(aes(x = max(forest_data_sep$`Upper 95% CI`, na.rm = TRUE) * 1.15, label = hr_label),
            hjust = 0, size = 4, color = "black") +
  scale_shape_manual(values = c(sig = 16, ns = 1, ref = 18), guide = "none") +
  scale_x_log10(breaks = c(0.5, 1, 1.5, 2, 3),
                limits = c(NA, max(forest_data_sep$`Upper 95% CI`, na.rm = TRUE) * 2.6)) +
  labs(x = "Hazard ratio (log scale)", y = NULL) +      # title removed
  theme_minimal(base_size = 13) +
  theme(
    panel.grid = element_blank(),
    axis.line.x = element_line(color = "black", linewidth = 0.4),
    axis.ticks.x = element_line(color = "black", linewidth = 0.4),
    axis.text.y = element_text(size = 12, color = "black"),
    axis.text.x = element_text(size = 11, color = "black"),
    axis.title.x = element_text(size = 12, color = "black"),
    plot.title = element_blank(),               # no title on the figure
    plot.subtitle = element_blank(),
    plot.background = element_rect(fill = "white", color = NA),
    panel.background = element_rect(fill = "white", color = NA),
    plot.margin = margin(20, 60, 20, 20)
  )

forest_plot_sep

ggsave("forest_plot_separate.png", plot = forest_plot_sep,
       width = 8, height = 5, dpi = 600, bg = "white")

```
